NLIZE: a Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models

### 2018-03-26 paper/background.tex
update prediction section

At the first glance, the task of natural language inference may seem less practical compared to other common NLP challenges such as machine translation, however, the ability to distinguish entailment and contradiction relationship is fundamental to understanding natural language at large. 
%
Considering the ambiguousness of natural language and polysemy words, the inference task can become quite challenging (especially from learning algorithm's point of view). Take the following sentences as an example (here \textbf{P} refer to premise, \textbf{H} refer to hypothesis):  (\textbf{P}) Facebook's IPO electrified the general public; (\textbf{H1}) Facebook went public; (\textbf{H2}) General Electric went public; (\textbf{H3}) People ignored Facebook's IPO. The literal similarity between ``Electric'' and ``electrified'' may trick the model to predict \textbf{H2} as \emph{entailment}. The model likely will also fail to understand the link between ``went public'' and ``IPO'', therefore, mistake \textbf{H1} as \emph{neutral}.
%
%The grand challenge in Natural Language Processing (NLP) is to have machine to acquire
%deep comprehension of textual information. Major tasks include Natural Language Inference,
%Machine Translation, Questions Answering, Summarization, and etc.
%Recently, neural networks models have performed strongly on these tasks.
%
Recently, Bowman et al. introduce a large corpus~\cite{BowmanAngeliPotts2015} for the NLI task, which helps spawn a new wave of effective neural network based NLI models. In this work, we focus on the analysis of the decomposable attention model~\cite{parikh2016emnlp} on this dataset.

>>>>

At the first glance, the task of natural language inference may seem less practical compared to other well-known NLP challenges such as machine translation, however, the ability to distinguish entailment and contradiction relationship is fundamental to understanding natural language at large. 
%
Considering the ambiguousness of natural language and polysemy words, the inference task can become quite challenging (especially from learning algorithm's point of view). Take the following sentences as an example (here \textbf{P} refers to premise, \textbf{H} refers to hypothesis):  (\textbf{P}) Facebook's IPO electrified the general public; (\textbf{H1}) Facebook went public; (\textbf{H2}) General Electric went public; (\textbf{H3}) People ignored Facebook's IPO. The literal similarity between ``Electric'' and ``electrified'' may trick the model to predict \textbf{H2} as \emph{entailment}. The model likely will also fail to understand the link between ``went public'' and ``IPO'', therefore, mistake \textbf{H1} as \emph{neutral}.
%
%The grand challenge in Natural Language Processing (NLP) is to have machine to acquire
%deep comprehension of textual information. Major tasks include Natural Language Inference,
%Machine Translation, Questions Answering, Summarization, and etc.
%Recently, neural networks models have performed strongly on these tasks.
%
Recently, Bowman et al. introduce a large corpus~\cite{BowmanAngeliPotts2015} for the NLI task, which helps spawn a new wave of effective neural network based NLI models. In this work, we focus on the analysis of the decomposable attention model~\cite{parikh2016emnlp} on this dataset.
